A Look at Implementing Councurrent Hash Tables in Java

### 2022-03-25 paper.tex
Added Last Name
Conversion to IEEE formatting

\documentclass{article}

\usepackage{listings}
\usepackage{hyperref}

\begin{document}
\author{Dalton Kajander, Shawn Guydeene, Blake Lastname}
\title{Concurrent Hash Tables in Java}
\date{\today{}}
\maketitle

\newpage
\tableofcontents
\newpage

\section{The Problem}
What problem?

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{listings}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{A Look at Implementing Councurrent Hash Tables in Java}

\author{\IEEEauthorblockN{ Shawn Guydeene}
\and
\IEEEauthorblockN{ Dalton Kajander}
\and
\IEEEauthorblockN{ Blake Celestian}
}

\maketitle

\begin{abstract}
Abstract goes here.
\end{abstract}

\begin{IEEEkeywords}
Concurrent Programming, Hash-table representations
\end{IEEEkeywords}

\section{The Problem}
Our group looked into the creation of hash tables in Java, and how one would be able to
